\section{Evaluation}

For the user Evaluation, we prepared some tasks to be concluded, starting from the search for specific results, inspection of the document, user relevance feedback, and then repeat. Limited suggestions and help were given during the process and the results were then kept through questionnaires.

\subsection{Evaluation design and methodology}

The evaluation aimed to gauge the usability and user experience of the beer-search-engine through a structured approach. Three participants were selected to perform tasks on the system within a limited time frame of three minutes each. The classic workflow of the retrieval system was followed, allowing users to familiarize themselves with its functionalities. This was followed by the completion of the System Usability Scale (SUS) and User Experience (UX) questionnaires

\subsection{System Usability Scale (SUS) questionnaire}

The SUS questionnaire was administered immediately after the user interaction with the beer-search-engine. Participants were asked to rate the system's usability on a scale from 1 to 5, with 5 indicating strong agreement. Scores were then normalized to generate an overall SUS score. The three users

\subsection{User Experience (UX) questionnaire}

In addition to the SUS questionnaire, participants were provided with a UX questionnaire to capture subjective experiences, emotions, and overall satisfaction with the beer-search-engine. The questionnaire comprised a range of Likert scale questions aimed at uncovering 26 specific aspects of the user experience.

\subsection{Outcome}

The evaluation revealed a generally positive user sentiment towards our beer-search-engine. While users appreciated its functionality and capabilities, areas for improvement were highlighted, including interface clarity, navigation cues, and information organization. Furthermore, all the users were able to complete all the tasks assigned to them without any aid or with small aid. These findings serve as valuable insights for refining the system and enhancing overall usability and user experience.